---
title: "Tutorials on RNA-Seq Data Analysis"
author:
- name: Nicolas Delhomme
  affiliation: UPSC
  email: nicolas.delhomme@umu.se
package: RnaSeqTutorial02
output:
  BiocStyle::html_document
abstract: |
  This is the second in a series of tutorials to learn about data science in R, perform an
  RNA-Seq Exploratory Data Analysis, a Differential Gene Expression analysis, a
  Differential Transcript Usage analysis, a Gene Set Enrichment Analysis and an
  ensemble approach thereof.

vignette: |
  %\VignetteIndexEntry{RnaSeqTutorial02}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Getting started

This is the second of a series of tutorials. It performs the exploratory data analysis of a public RNA-Seq dataset.

To start the tutorial run:
```{r tutorial, eval=FALSE}
learnr::run_tutorial("02_exploratory_data_analysis", package = "RnaSeqTutorial02")
```

# Accessing the code

## Tutorials

The tutorial is available as a `.Rmd` file in the `tutorials` directory:

```{r tutorial list}
dir(system.file(package="RnaSeqTutorial02","tutorials"))
```

```{r tutorial paths}
list.files(path=system.file(package="RnaSeqTutorial02","tutorials"),
           pattern="*.Rmd",
           recursive=TRUE)
```

## Scripts

There is a script available in the `script` directory, associated with the tutorial.

```{r script paths}
list.files(path=system.file(package="RnaSeqTutorial02","scripts"),
           pattern="*.R",
           recursive=TRUE)
```

# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
